### 2022-08-01 main.tex
ttweak

\begin{flushleft}{
	\Large
	\textbf\newline{
		Intermediate levels of asymptomatic transmission can lead to the highest levels of epidemic fatalities
	}
}
\newline
\\
Sang Woo Park\textsuperscript{1},
Bryan T. Grenfell\textsuperscript{1,2},
Jonathan Dushoff\textsuperscript{3,4,5},
Joshua S. Weitz\textsuperscript{6,7,8,*}
\\
\bigskip
\textbf{1} Department of Ecology and Evolutionary Biology, Princeton University, Princeton, NJ, USA
\\
\textbf{2} Princeton School of Public and International Affairs, Princeton University, Princeton, NJ, USA
\\
\textbf{3} Department of Biology, McMaster University, Hamilton, ON, Canada
\\
\textbf{4} Department of Mathematics and Statistics, McMaster University, Hamilton, ON, Canada
\\
\textbf{5} M.\,G.\,DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, ON, Canada
\\
\textbf{6} School of Biological Sciences, Georgia Institute of Technology, Atlanta, GA, USA
\\
\textbf{7} School of Physics, Georgia Institute of Technology, Atlanta, GA, USA
\\
\textbf{8} Institut de Biologie, \'{E}cole Normale Sup\'{e}rieure, Paris, France
\\
\bigskip

>>>>

\begin{flushleft}{
	\Large
	\textbf\newline{
		Intermediate levels of asymptomatic transmission can lead to the highest levels of epidemic fatalities
	}
}
\newline
\\
Sang Woo Park\textsuperscript{1},
Jonathan Dushoff\textsuperscript{2,3,4},
Bryan T. Grenfell\textsuperscript{1,5},
Joshua S. Weitz\textsuperscript{6,7,8,*}
\\
\bigskip
\textbf{1} Department of Ecology and Evolutionary Biology, Princeton University, Princeton, NJ, USA
\\
\textbf{2} Department of Biology, McMaster University, Hamilton, ON, Canada
\\
\textbf{3} Department of Mathematics and Statistics, McMaster University, Hamilton, ON, Canada
\\
\textbf{4} M.\,G.\,DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, ON, Canada
\\
\textbf{5} Princeton School of Public and International Affairs, Princeton University, Princeton, NJ, USA
\\
\textbf{6} School of Biological Sciences, Georgia Institute of Technology, Atlanta, GA, USA
\\
\textbf{7} School of Physics, Georgia Institute of Technology, Atlanta, GA, USA
\\
\textbf{8} Institut de Biologie, \'{E}cole Normale Sup\'{e}rieure, Paris, France
\\
\bigskip
